Bootstrap Confidence Intervals for Sharp Regression Discontinuity Designs

### 2016-08-03 main_paper.tex
Make small refinement to Theorem 2
We should be clear that the distributional convergence in Theorem 2 is
uniform across tau. That's not necessary in Theorem 1 because the limit
is normal so convergence is automatically uniform across different
values of the mean. In Theorem 2 we're not explicit that the limit is
normal so we should be explicit about uniformity.
Redefine notation in appendix with kernel weights
Overdue :)
Minor wording tweak in Theorem 1's proof
Extend and tweak notation defined in appendix
This commit has two main features
- Adds population versions of some of the estimated c

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$,
\begin{align*}
  (\hat{\mu}_{+,p}(h),\ \hat{\mu}_{+,p}^{(1)}(h),\dots,\ \hat\mu_{+,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[+]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2 \\
  (\hat{\mu}_{-,p}(h),\ \hat{\mu}_{-,p}^{(1)}(h),\dots,\ \hat\mu_{-,p}^{(p)}(h))'
  &= \argmin_{\beta} \ssum[-]{i}{h} (Y_i - r_p(X_i/h)'\beta)^2
\end{align*}
and
\begin{align*}
  \Gamma_{+,p}(h) &= \tfrac{1}{nh} \ssum[+]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Gamma_{-,p}(h) &= \tfrac{1}{nh} \ssum[-]{i}{h} r_p(X_i/h) r_p(X_i/h)' \\
  \Psi_{+,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[+]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Psi_{-,p,q}(h,b)
  &= \tfrac{1}{nhb} \ssum[-]{i}{\min(h,b)} r_p(X_i/h) r_q(X_i/b)'
    \V(Y_i \mid X_i) \\
  \Bf_+(h)
  & = e_0' \Gamma_{+,1}^{-1}(h)
    \ssum[+]{i}{h} r_1(X_i/h) \; X_i^2 / h^2, \\
  \Bf_-(h)
  & = e_0' \Gamma_{-,1}^{-1}(h)
    \ssum[-]{i}{h} r_1(X_i/h) \; X_i^2 / h^2.
\end{align*}

Also, for reference, define the variance terms
\begin{equation*}
  V(h)
  = e_0' \Big(\tfrac{1}{n} \Gamma_{-,1}^{-1} \Psi_{-,1} \Gamma_{-,1}^{-1}
  + \tfrac{1}{n} \Gamma_{+,1}^{-1} \Psi_{+,1} \Gamma_{+,1}^{-1}\Big) e_0
\end{equation*}
and
\begin{multline*}
  C(h,b) =
  n^{-1} e_2' \Big[
    \Gamma_{+,2}^{-1}(b) \Psi_{+,2,2}(b,b) \Gamma_{+,2}^{-1}(b) \Bf^2_+(h) +
    \Gamma_{-,2}^{-1}(b) \Psi_{-,2,2}(b,b) \Gamma_{-,2}^{-1}(b) \Bf^2_-(h)
    \Big] e_2 \\
  - 2 h^2 n^{-1} b^{-2}
    e_0' \Big[
    \Gamma^{-1}_{+,1}(h) \Psi_{+,1,2}(h,b) \Gamma_{+,2}^{-1}(b) \Bf_+(h) +
    \Gamma^{-1}_{-,1}(h) \Psi_{-,1,2}(h,b) \Gamma_{-,2}^{-1}(b) \Bf_-(h)
    \Big] e_2.
\end{multline*}
See CCT for the motivation and derivation of these formulas.

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{align*}
  \hat\beta^*_{+,p} - \beta^*_{+,p}
  & = \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{+,h}(X_i) \Big)^{-1}
  \sum_{i = 1}^n r_p(X_i) K_{+,h}(X_i) \hat\varepsilon_i e_i^* \\
  \hat\beta^*_{-,p} - \beta^*_{-,p}
  &= \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{-,h}(X_i)\Big)^{-1}
  \sum_{i = 1}^n r_p(X_i) K_{-,h}(X_i) \hat\varepsilon_i e_i^*
\end{align*}
ensuring that
\begin{align*}
  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely and, consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_+^{*(2)} = \hat\mu_{+,2}^{(2)}(b)$ and
$\mu_-^{*(2)} = \hat\mu_{-,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$,
$\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}$, and
$\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:6} for
the iterated bootstrap to get
\begin{align*}
  \hat\tau^{*}(h) - &\Delta^{**}(h,b) - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_{-,2}^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{+}^{*} =
(\varepsilon_{+,1}^{*},\dots,\varepsilon_{+,M_+(b)}^{*})'$ and
$\Omega_+(h,b)$ is an $M_+(b)$-dimensional vector with $i$th element
$\Omega_{+,1i}(h,b) - \Omega_{+,2i}(h,b)$, which are defined as
\begin{align*}
  \Omega_{+,1i}(h,b) &=
  (1\quad 0)
  \Big(\ssum[+]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m_+(b,i)} / h) \1\{h > X_{m_+(b,i)} \geq 0\}
\intertext{and}
  \Omega_{+,2i}(h,b) &= (0\quad 0 \quad h^2)
  \Big(\ssum[+]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m_+(b,i)} / b).
\end{align*}
The definitions of $\epb_{-}^{*}$ and $\Omega_-(h,b)$ have the same
definitions as $\epb_{+}^{*}$ and $\Omega_+(h,b)$ after making the
obvious substitutions of ``$-$'' for ``$+$.''

Notice that~\eqref{eq:6} implies that
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau
  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
\end{equation*}
with $\epb_+$ an i.i.d. random vector of length $M_+(b)$, the $i$th
element of which is distributed as
\[
  \varepsilon_{+,i} =^d
  \begin{cases}
    Y_{m_+(1,b)} - \E(Y_{m_+(1,b)} \mid X_{m_+(1,b)})
    & \text{with probability\ } 1/M_+(b) \\
    \vdots \\
    Y_{m_+(M_+(b),b)} - \E(Y_{m_+(M_+(b),b)} \mid X_{m_+(M_+(b),b)})
    & \text{with probability\ } 1/M_+(b),
  \end{cases}
\]
and $\epb_-$ the corresponding quantity after replacing ``+'' with
``--.''  Consequently, it suffices to prove that
\begin{gather}
  \label{eq:7}
  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
    V'(h,b)^{-1/2}\Omega_+(h,b)'\epb_{+}) \to^p 0
  \intertext{and}
  \label{eq:8}
  \rho(V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}^{*},\
    V'(h,b)^{-1/2}\Omega_-(b)'\epb_{-}) \to^p 0
\end{gather}
with $\rho$ the ``Mallows metric'' used by
\citet{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments,
  $\rho(u, v)$ is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}
Convergence in $\rho$ is equivalent to convergence in both distribution
and second moments. \citep[Lemma 8.3.]{bickel1981}

We will only prove~\eqref{eq:7} since the proof of~\eqref{eq:8} is
identical. By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}^{*},\
  &V'(h,b)^{-1/2} \Omega_+(h,b)'\epb_{+}) \\
  &\leq \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times
    \tr(V'(h,b)^{-1/2} \Omega_+(h,b)' \Omega_+(h,b)V'(h,b)^{-1/2}) \\
  &= \rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{+,1}^{*}, \varepsilon_{+,1}) \to^{p^{*}} 0$. Let
$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
realized values of $\epb_+$ with replacement and let
$\bar{\varepsilon}^\circ = (1/M_+(b)) \osum[+]{i}{b} \varepsilon^\circ_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{+,1}^*, \varepsilon_{+,1})
  \leq
  \Big((\bar\varepsilon^{\circ})^2 +
  (2/M_+(b)) \osum[+]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
  + \rho(\varepsilon^\circ_1,\ \varepsilon_{+,1}).
\end{equation*}
But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
\[
  (1/M_+(b)) \osum[+]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\varepsilon_1^\circ,\ \varepsilon_{+,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed

>>>>

\appendix
\section{Mathematical appendix}
Let $e_p$ be the selection vector with 1 in element $p+1$ and 0
everywhere else. Much of the theory in this appendix applies to both
sides of the cutoff symmetrially, so we will use a ``$\bullet$'' as a
placeholder for either $+$ or $-$ in equations; i.e.\ the equation
\[
  \hat\mu_\bullet(h) = \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{\bullet,h}(X_i)
\]
would define both $\hat\mu_+(h)$ and $\hat\mu_-(h)$ as
\begin{align*}
  \hat\mu_+(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{+,h}(X_i) \\
  \hat\mu_-(h) &= \argmin_{\mu} \min_{\beta} \sum_{i=1}^n
  (Y_i - \mu - \beta X_i)^2 K_{-,h}(X_i).
\end{align*}
Define the following additional notation:\footnote{%
  As we mention in Section~\ref{background}, we have adopted CCT's
  notation where possible and these terms originate in that paper.} %
$r_p(x) = (1,\ x,\dots,\ x^p)'$, $\1_+(x) = \1\{x > 0\}$, $\1_-(x) = \1\{x \leq 0\}$,
\begin{align*}
  \Gamma_{\bullet,p}(h)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_p(X_i/h)' K_{\bullet,h}(X_i) \\
  \Bf_\bullet(h)
  & = e_0' \big(\Gamma_{\bullet,1}(h)\big)^{-1}
    \tfrac{1}{n} \sum_{i=1}^n (X_i / h)^2 r_1(X_i/h) K_{\bullet,h}(X_i) \\
  \Psi_{\bullet,p,q}(h,b)
  &= \tfrac{1}{n} \sum_{i=1}^n r_p(X_i/h) r_q(X_i/b)'
     K_{\bullet,h}(X_i) K_{\bullet,b}(X_i) \V(Y_i \mid X_i)
\end{align*}
as well as their population counterparts,
\begin{align*}
  \Gammat_{\bullet,p}(h) &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) f(h u) \1_\bullet(u) du \\
  \Gamma_{\bullet,p} &= \int_{-\infty}^\infty   r_p(u) r_p(u)' K(u) \1_\bullet(u) du \\
  \Psit_{\bullet,p,q}(h,b) &= \int_{-\infty}^\infty
     r_p(\tfrac{m}{h} u) r_q(\tfrac{m}{b} u)' K(\tfrac{m}{b} u) K(\tfrac{m}{h} u)
     \V(Y_i \mid X_i = um) f(um) \1_\bullet(u) du \\
  \Psi_{\bullet,p} &= \int_{-\infty}^\infty
     r_p(u) r_p(u)' K(u)^2 \1_\bullet(u) du
\end{align*}
Remember that $f$ is the pdf of the running variable and $m = \min(h,b)$. Lemmas
SA1 and SA2 of CCT imply that all of these terms have well-defined limits under
Assumptions~\ref{A1} and~\ref{A2} (for some, after normalization), namely that
the following relationships hold:
\begin{align}
  \Gamma_{\bullet,p}(h) & = \Gammat_{\bullet,p}(h) + o_p(1) &
  \Gammat_{\bullet,p}(h) &= f(0) \, \Gamma_{\bullet,p} + o(1) \label{eq:10} \\
  \tfrac{hb}{m} \Psi_{\bullet,p,q}(h, b) &= \Psit_{\bullet,p,q}(h,b) + o_p(1) &
  \Psit_{\bullet,p,p}(h,h) &= f(0) \, \sigma^2_{\bullet}(0) \, \Psi_{\bullet,p} + o(1) \label{eq:12}
\end{align}
Implicitly the right column of equations holds as $h \to 0$.

Also let $\hat\beta_{\bullet,p}(h)$ be the coefficient
estimators from the weighted regression of $Y_i$ on $r_p(X_i)$. As in CCT, this
implies that
\begin{align*}
  \hat\beta_{\bullet,p}(h) &= H_p \big(\Gammat_{\bullet,p}(h)\big)^{-1}
    \sum_{i=1}^n r_p(X_i/h) Y_i K_{\bullet,h}(X_i)
\end{align*}
with $H_p(h) = \diag(1, h^{-1}, \dots, h^{-p})$.
These coefficients are related to the quantities of interest by
\begin{equation*}
  \hat{\mu}_{\bullet,p}^{(\nu)}(h) = \nu! e_\nu' \hat\beta_{\bullet,p}(h).
\end{equation*}
for $\nu = 0,\dots,p$.

For reference, define the variance terms
\begin{equation*}
  V(h)
  = \tfrac{1}{n} e_0' \big(\Gamma_{-,1}(h)^{-1} \Psi_{-,1,1}(h,h)
    \Gamma_{-,1}(h)^{-1}
  + \Gamma_{+,1}(h)^{-1} \Psi_{+,1,1}(h,h) \Gamma_{+,1}(h)^{-1} \big) e_0
\end{equation*}
and
\begin{multline*}
  C(h,b) =
  \tfrac{1}{n} \, e_2' \big[
    \Gamma_{+,2}(b)^{-1} \Psi_{+,2,2}(b,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h)^2 +
    \Gamma_{-,2}(b)^{-1} \Psi_{-,2,2}(b,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)^2
  \big] e_2 \\
  - \tfrac{2 h^2}{n b^{2}}
    e_0' \Big[
    \Gamma_{+,1}(h)^{-1} \Psi_{+,1,2}(h,b) \Gamma_{+,2}(b)^{-1} \Bf_+(h) +
    \Gamma_{-,1}(h)^{-1} \Psi_{-,1,2}(h,b) \Gamma_{-,2}(b)^{-1} \Bf_-(h)
    \Big] e_2.
\end{multline*}
See CCT for more on the motivation and derivation of these formulas.

\subsection{Proof of Theorem~\ref{T1}}
We have
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau = (\hat\tau(h) - \E \hat \tau(h)) +
  (\E \hat \tau(h) - \tau) - (\E^* \hat \tau^*(h) - \tau^*).
\end{equation*}
By construction,
\begin{align*}
  \hat\beta^*_{+,p} - \beta^*_{+,p}
  & = \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{+,h}(X_i) \Big)^{-1}
  \sum_{i = 1}^n r_p(X_i) K_{+,h}(X_i) \hat\varepsilon_i e_i^* \\
  \hat\beta^*_{-,p} - \beta^*_{-,p}
  &= \Big(\sum_{i = 1}^n r_p(X_i) r_p(X_i)' K_{-,h}(X_i)\Big)^{-1}
  \sum_{i = 1}^n r_p(X_i) K_{-,h}(X_i) \hat\varepsilon_i e_i^*
\end{align*}
ensuring that
\begin{align*}
  \E^* \hat\mu_{+,1}^*(h) - \mu_{+}^{*}
  &= h^{2} \mu_{+}^{*(2)} \Bf_{+}(h)/2,
  &\E^* \hat\mu_{-,1}^*(h) - \mu_{-}^{*}
  &= h^{2} \mu_{-}^{*(2)} \Bf_{-}(h)/2,
\end{align*}
almost surely and, consequently,
\begin{equation*}
  \E^* \hat\tau^*(h) - \tau^{*} = h^2\, \mu_+^{*(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{*(2)} \Bf_{-}(h)/2.
\end{equation*}
CCT's Lemma A1 implies that
\begin{equation*}
  \E \hat\tau(h) - \tau = h^2\, \mu_+^{(2)} \Bf_+(h)/2
  - h^2\, \mu_{-}^{(2)} \Bf_{-}(h)/2 + O_p(h^3)
\end{equation*}
as well, giving
\begin{align}
  \hat\tau(h) - & \E \hat\tau(h) + (\E \hat\tau(h) - \tau) - (\E^* \hat\tau^*(h) - \tau^*)\notag \\
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 \big((\mu_{-}^{*(2)} - \mu_{-}^{(2)}) \Bf_{-}(h) /2
   - (\mu_+^{*(2)}-\mu_+^{(2)}) \Bf_{+}(h) / 2 \big) + O_p(h^{3}) \notag \\
  \label{eq:6}
  &= \hat\tau(h) - \E\hat\tau(h)
   + h^2 (\hat\mu_{-,2}^{(2)}(b) - \mu_-^{(2)}) \Bf_{-}(h) /2 \\
  \notag
  &\pushright{- h^2 (\hat\mu_{+,2}^{(2)}(b) - \mu_+^{(2)}) \Bf_{+}(h) / 2
   + O_p(h^{3})}
\end{align}
The second equality holds because
$\mu_\bullet^{*(2)} = \hat\mu_{\bullet,2}^{(2)}(b)$ almost surely. Asymptotic
normality then follows from normality of $\hat\tau(h) - \E\hat\tau(h)$ and
$\hat\mu_{\bullet,2}^{(2)}(b) - \mu_\bullet^{(2)}$ using similar arguments to
CCT's Lemma SA4.D.\qed

\subsection{Proof of Theorem~\ref{T2}}
Repeat the steps from Theorem~\ref{T1}'s proof through~\eqref{eq:6} for
the iterated bootstrap to get
\begin{align*}
  \hat\tau^{*}(h) - &\Delta^{**}(h,b) - \tau^*
  = (\hat\tau^*(h) - \E^* \hat \tau^*(h)) +
  (\E^* \hat \tau^*(h) - \tau^*) - (\E^{**} \hat \tau^{**}(h) - \tau^{**}) \\
  &= \hat\tau^*(h) - \E^*\hat\tau^*(h)
   + h^2 (\hat\mu_{-,2}^{*(2)}(b) - \mu_-^{*(2)}) \Bf_{-}(h) /2
   - h^2 (\hat\mu_{+,2}^{*(2)}(b) - \mu_+^{*(2)}) \Bf_{+}(h) / 2 \\
  &= \Omega_{+}(h,b)' \epb_{+}^{*} - \Omega_{-}(h,b)' \epb_{-}^{*},
\end{align*}
where
$\epb_{\bullet}^{*} =
(\varepsilon_{\bullet,1}^{*},\dots,\varepsilon_{\bullet,M_\bullet(b)}^{*})'$ and
$\Omega_\bullet(h,b)$ is an $M_\bullet(b)$-dimensional vector with $i$th element
$\Omega_{\bullet,1i}(h,b) - \Omega_{\bullet,2i}(h,b)$, which are defined as
\begin{align*}
  \Omega_{\bullet,1i}(h,b) &=
  (1\quad 0)
  \Big(\ssum[\bullet]{j}{h} r_1(X_j / h) r_1(X_j / h)' \Big)^{-1}
    r_1(X_{m_\bullet(b,i)} / h) \1\{h > X_{m_\bullet(b,i)} \geq 0\}
\intertext{and}
  \Omega_{\bullet,2i}(h,b) &= (0\quad 0 \quad h^2)
  \Big(\ssum[\bullet]{j}{b} r_2(X_j / b) r_2(X_j / b)' \Big)^{-1}
    r_2(X_{m_\bullet(b,i)} / b).
\end{align*}

Notice that~\eqref{eq:6} implies that
\begin{equation*}
  \hat\tau(h) - \Delta^*(h,b) - \tau
  =^d \Omega_{+}(h,b)' \epb_{+} - \Omega_{-}(h,b)' \epb_{-} + O_p(h^3),
\end{equation*}
with $\epb_\bullet$ an i.i.d. random vector of length $M_\bullet(b)$, the $i$th
element of which is distributed as
\[
  \varepsilon_{\bullet,i} =^d
  \begin{cases}
    Y_{m_\bullet(1,b)} - \E(Y_{m_\bullet(1,b)} \mid X_{m_\bullet(1,b)})
    & \text{with probability\ } 1/M_\bullet(b) \\
    \vdots \\
    Y_{m_\bullet(M_\bullet(b),b)} - \E(Y_{m_\bullet(M_\bullet(b),b)} \mid X_{m_\bullet(M_\bullet(b),b)})
    & \text{with probability\ } 1/M_\bullet(b).
  \end{cases}
\]
Consequently, it suffices to prove that
\begin{equation}
  \label{eq:7}
  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
    V'(h,b)^{-1/2}\Omega_\bullet(h,b)'\epb_{\bullet}) \to^p 0
\end{equation}
with $\rho$ the ``Mallows metric'' used by
\citet{bickel1981}.\footnote{%
  For two random vectors $u$ and $v$ with finite 2nd moments,
  $\rho(u, v)$ is defined as
  \begin{equation*}
    \rho(u, v) = \inf\nolimits_{(U, V)\ s.t.\ U =^d u,\ V =^d v}
    \big(\E \lVert U - V \rVert^2\big)^{1/2}.
  \end{equation*}}
Convergence in $\rho$ is equivalent to convergence in both distribution
and second moments. \citep[Lemma 8.3.]{bickel1981}

By Theorem 2.1 of \cite{freedman1981}, we have
\begin{align*}
  \rho(V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}^{*},\
  &V'(h,b)^{-1/2} \Omega_\bullet(h,b)'\epb_{\bullet}) \\
  &\leq \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times
    \tr(V'(h,b)^{-1/2} \Omega_\bullet(h,b)' \Omega_\bullet(h,b)V'(h,b)^{-1/2}) \\
  &= \rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \times O_{p^{*}}(1),
\end{align*}
the second line holding as a consequence of CCT's Lemma SA1. So it suffices
to show that $\rho(\varepsilon_{\bullet,1}^{*}, \varepsilon_{\bullet,1}) \to^{p^{*}} 0$. Let
$\varepsilon^\circ_i$ be an i.i.d. sequence randomly drawn from the
realized values of $\epb_\bullet$ with replacement and let
$\bar{\varepsilon}^\circ = (1/M_\bullet(b)) \osum[\bullet]{i}{b} \varepsilon^\circ_i$. Then,
using the same arguments as \cite{freedman1981}, we have the upper bound
\begin{equation*}
  \rho(\varepsilon_{\bullet,1}^*, \varepsilon_{\bullet,1})
  \leq
  \Big((\bar\varepsilon^{\circ})^2 +
  (2/M_\bullet(b)) \osum[\bullet]{i}{b} (\hat\varepsilon_i - \varepsilon_i)^2\Big)^{1/2}
  + \rho(\varepsilon^\circ_1,\ \varepsilon_{\bullet,1}).
\end{equation*}
But $(\bar\varepsilon^{\circ})^2 \to^p 0$ by the LLN,
\[
  (1/M_\bullet(b)) \osum[\bullet]{i}{b}
  \E((\hat\varepsilon_i - \varepsilon_i)^2 \mid X_i) \to 0
\]
by CCT's Lemma SA1, and
$\rho(\varepsilon_1^\circ,\ \varepsilon_{\bullet,1}) \to^p 0$ by Lemma~8.4 of
\cite{bickel1981}.\qed
